The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-02-16 paper/main.tex
improve text (minor)

Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
\begin{itemize}
%
\item If single, primary, and secondary stars all host the same number
  of planets per star, and the planet radius distribution is a power
    law with the exponent reported by~\citet{howard_planet_2012} at $r
    > 2r_\oplus$, then binarity influences apparent planet occurrence
    rates at the few percent level. This applies for apparent radii
    from $2r_\oplus$ to $17r_\oplus$ (Section~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with the
  \citet{howard_planet_2012} exponent above $2r_\oplus$ and a constant
    occurrence below $2r_\oplus$, the rate density for radii below
    $2r_\oplus$ is overestimated. The overestimate, $\Delta \Gamma_0 =
    |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach $50\%$
    (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is smaller
    than current systematic uncertainties on the occurrence rates of
    Earth-sized planets, this implies that binarity could eventually
    become an important component of the $\eta_\oplus$ error budget.
%
\item Binarity blurs sharp features in the radius distribution
  (Figure~\ref{fig:model_4}), to a degree that could affect precise
    measurements of the depth, width, and slope of
    the~\citet{fulton_california-_2017} radius gap.
    %in the event that
    %planets are not carefully vetted with high-resolution imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates
  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
    radius distribution, similar to that reported
    by~\citet{petigura_CKS_2017}.
%
\item Detected planets with $r\a \gtrsim 0.5r_\oplus$ that are
  revealed by high-resolution imaging surveys to exist in binaries are
    more likely to orbit the primary (Figure~\ref{fig:frac_model_3}).
%
\item Near the break in occurrence as a function of planet
  radius at $2r_\oplus$, the fraction of detected planets with
    binary companions should increase by roughly $5$~to~$10\%$
    (Figure~\ref{fig:frac_model_3}).
\end{itemize}

>>>>

Applying Equation~\ref{eq:general_Gamma_a}, we then showed that:
\begin{itemize}
%
\item If single, primary, and secondary stars all host the same number
  of planets per star, and the planet radius distribution is a power
    law with the exponent reported by~\citet{howard_planet_2012}, then
    binarity influences apparent planet occurrence rates at the few
    percent level. This applies for apparent radii from $2r_\oplus$ to
    $17r_\oplus$ (Section~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with the
  \citet{howard_planet_2012} exponent above $2r_\oplus$ and a constant
    occurrence below $2r_\oplus$, the rate density for radii below
    $2r_\oplus$ is overestimated. The magnitude of the error, $\Delta
    \Gamma_0 = |\Gamma_0 - \Gamma\a|/\Gamma_0$, can easily reach
    $50\%$ (Figure~\ref{fig:occ_rate_model_3_log}).  Although this is
    smaller than current systematic uncertainties on the occurrence
    rates of Earth-sized planets, this implies that binarity could
    eventually become an important component of the $\eta_\oplus$
    error budget.
%
\item Binarity blurs sharp features in the radius distribution
  (Figure~\ref{fig:model_4}), to a degree that could affect precise
    measurements of the depth, width, and slope of
    the~\citet{fulton_california-_2017} radius gap.
    %in the event that
    %planets are not carefully vetted with high-resolution imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates
  (Figure~\ref{fig:gaussian_HJ}).  This assumes a Gaussian planet
    radius distribution, similar to that reported
    by~\citet{petigura_CKS_2017}.
%
\item Detected planets with apparent radii greater than $0.5r_\oplus$
  that are revealed by high-resolution imaging surveys to exist in
    binaries are more likely to orbit the primary
    (Figure~\ref{fig:frac_model_3}).
%
\item Near the break in occurrence as a function of planet
  radius at $2r_\oplus$, the fraction of detected planets with
    binary companions should increase by roughly $5$~to~$10\%$
    (Figure~\ref{fig:frac_model_3}).
\end{itemize}
